Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
small fix sec 4.2

In Fig.~\ref{fig:CEGIS}, we illustrate the second approach, which 
uses a two-stage verification such that in the first stage we 
assume a certain precision \param{I_b}{F_b}  
followed by checking the soundness of our assumption
in a second verification stage.

>>>>

The second approach is illustrated in Fig.~\ref{fig:CEGIS} and 
uses a two-stage verification such that in the first stage we 
assume a certain precision \param{I_b}{F_b}  
followed by checking the soundness of our assumption
in a second verification stage.
